How Significant was WW2 in the Development of the Computer?

### 2017-02-03 Draft 2/Section 2 - Turing Machines.tex
Tiny description
Added recursive syntax

\medskip
In each of these, the first argument \textit{a} is observed, and an action which either writes a \texttt{1} or \texttt{0}, or copies or negates from \textit{b} depending on the truth tables, in a very similar manner to $\lambda$-calculus. Gradually, the cryptic and simplified language of Finite State Machines is yielding results similar to that of a computer.

\subsubsection{Simplified Configurations}

As we have moved into more and more complex FSM functions, it can be noted that the middle two columns of the FSM are becoming gradually more scarce - this is due to the fact that their operation can be entirely represented within \textit{m}-functions. We have started doing so with the functions $\mathbb{l}$, $\mathbb{r}$, $\mathbb{p0}$, and $\mathbb{p1}$ - furthermore, it is not difficult to create conditional functions to replicate the operation of the second column.

@@

Since we have now entirely defined the operation of the machine in terms of functions, we no longer have any need for tables.

\end{document}

>>>>

\medskip
In each of these, the first argument \textit{a} is observed, and an action which either writes a \texttt{1} or \texttt{0}, or copies or negates from \textit{b} depending on the truth tables, in a very similar manner to $\lambda$-calculus. Gradually, the cryptic and simplified language of Finite State Machines is yielding results similar to that of a computer.
As we have moved into more and more complex FSM functions, it can be noted that the middle two columns of the FSM are becoming gradually more scarce - this is due to the fact that their operation can be entirely represented within \textit{m}-functions. We have started doing so with the functions $\mathbb{l}$, $\mathbb{r}$, $\mathbb{p0}$, and $\mathbb{p1}$ - furthermore, it is not difficult to create conditional functions to replicate the operation of the second column.

@@

The function $\mathbb{if}$ takes a symbol argument, which is compared to the symbol under the cursor - if they are the same, the machine $\rightarrow \mathbb{I}$; if not the machine $\rightarrow \mathbb{O}$.
Since we have now entirely defined the operation of the machine in terms of functions (as loops can be done with recursion), we no longer have any need for tables - in effect, we have built a purely functional programming language in terms of a simple finite state machine. Now, in order to define more \textit{m}-functions we no longer have to write a table:

\begin{lstlisting}
ifp(r,c,I,O,E) = fl(
    if(c,
        I,
        O
    ),
    E,
    r
)
\end{lstlisting}

Admittedly not the cleanest syntax, but still a simple one.
\end{document}
